A Review of\\ Adversarial Machine Learning\\ \huge{(4th ACM Workshop on AISec, Oct. 2011,43-58)}

### 2019-09-20 MTech/IC601/Assgnt2_Ppr_Rvw/Paper_Review.tex
Modified Review

Listed below are the milestones covered by the paper: 
\begin{itemize}
\item A very well-summarized overview of what Adversarial Machine Learning is, why it is necessary and relevant in this age, and how it can be accomplished.

@@

\item The two algorithms used as case studies are very much used in real life situations, and hence makes the paper very relevant in this day and age, thereby easily underlining the need for the topic researched on.

\item Privacy, being a trending concept throughout history and a fundamental human right, is also a part of this paper, and makes it a must-read for researchers in this field.
\end{itemize}
%------------------------------------------------
%
\section{Limitations}
\begin{itemize}
\item A section on image and pattern recognition, and how adversaries can trick such models, could have been made a part of the research, as it is a budding novel area in Machine Learning, and specifically, Deep Learning.
\item The paper is a bit too textual. Adding more images would have helped better illustrate the various attacks and countermeasures presented here.
\end{itemize}
%
%-----------------------------------------------------------------------
%
\section{Opinion}
~~~~~The paper gives a good introduction and an elaborate explanation on Adversarial Machine Learning, and how to counter it. It aptly highlights the necessity and relevance of securing learning models, especially when they will be planned to be used in mission-critical situations. However, a more generous use of images would've helped illustrate the attacks and countermeasures better.
%
%-----------------------------------------------------------------------

>>>>

Listed below are the milestones covered by the paper: 
\begin{itemize}
\item A good overview of Adversarial Machine Learning and its impact in the field of modern Artificial Intelligence.

@@

\item The two algorithms used as case studies are very much used in real life situations, and hence makes the paper very relevant in today's new age of Artificial Intelligence, thereby easily underlining the need for the topic researched on.

\item Privacy, being a trending concept throughout history and a fundamental human right, is also a part of this paper, and makes it a must-read for researchers in this field.
\end{itemize}
%------------------------------------------------
%
\section{Limitations}
\begin{itemize}
\item A section on image and pattern recognition, and how adversaries can trick such models, could have been made a part of the research, as it is a budding novel area in Machine Learning, and specifically, Deep Learning.
\item The paper is a bit too textual. Adding more images would have helped better illustrate the various attacks and countermeasures presented here.
\end{itemize}
%
%-----------------------------------------------------------------------
%
\section{Opinion}
~~~~~The paper gives a good introduction and an elaborate explanation on Adversarial Machine Learning, and how to counter it. It aptly highlights the necessity and relevance of securing learning models, especially when they will be planned to be used in mission-critical situations. However, the organization of the paper could be improved by including more references in the analyses.
%
%-----------------------------------------------------------------------
